---
output:
  knitrBootstrap::bootstrap_document:
    theme.chooser: TRUE
    highlight.chooser: TRUE
  html_document:
    toc: true
    theme: united
---

Help A. G.
=========

This document produces simulated data set similar to what A. G. has and runs the regressions covered in the TA session.

# Data

## Table

First, we create some simulated data for two machines with sales for 5 years.

```{r}
set.seed(20150331)
d <- data.frame(year = rep(2010:2014, each = 2), machine = factor(rep(c('EPIC', 'MP'), 5), levels = c('EPIC', 'MP')), sales = rnorm(10, 10000, 100))

## Manually make it so EPIC machine has higher sales and much higher after
## intervention
d$sales[d$machine == 'EPIC' & d$year < 2012] <- rnorm(2, 40000, 200)
d$sales[d$machine == 'EPIC' & d$year >= 2012] <- rnorm(3, 60000, 300)
d$intervention <- ifelse(d$year < 2012, 0, 1)

## Center year
d$yearCen <- d$year - 2010
knitr::kable(d, format = 'html', digits = 2)
```

## Vis

Next, we can visualize it.

```{r}
library('ggplot2')
ggplot(data = d, aes(x = year, y = sales, group = machine, colour = factor(intervention))) + geom_line() + geom_point()

ggplot(data = d, aes(x = year, y = sales, group = paste0(machine, intervention), colour = machine, shape = factor(intervention))) + geom_line() + geom_point()
```

# Regression

## Interaction

Using the EPIC machine as the reference group, we can use MLR to fit a model with interaction between intervention and the machine.


```{r}
f <- lm(sales ~ yearCen + factor(intervention)*machine, data = d)
summary(f)
```

Interpretations:

* Intercept: sales for year 2010 for machine EPIC
* yearCen: change in average sales for 1 year increase before the intervention, holding machine constant
* factor(intervention)1 + yearCen: change in average sales for 1 year increase for machine EPIC after the intervention
* machineMP + Intercept: sales for year 2010 for machine MP
* factor(intervention)1:machineMP + factor(intervention)1 + yearCen: change in average sales for 1 year increase for machine MP after the intervention

If _factor(intervention)1:machineMP_ is 0 that would mean that both machines have the same slopes after the intervention.

## No interaction


Or we can also fit the MLR without the machine variable (and also without the interaction term) for each of the machines.

```{r}
f.epic <- lm(sales ~ yearCen + factor(intervention), data = subset(d, machine == 'EPIC'))
summary(f.epic)

f.mp <- lm(sales ~ yearCen + factor(intervention), data = subset(d, machine == 'MP'))
summary(f.mp)
```

Interpretations (relative to each machine):

* Intercept: sales for year 2010
* yearCen: change in average sales for 1 year increase before the intervention
* factor(intervention)1 + yearCen: change in average sales for 1 year increase after the intervention

_factor(intervention)1_ is the change in the slope after the intervention.

# Stata

Next, lets export the data and re-do the analysis with Stata.

```{r}
write.table(d, file = 'helpAG.txt', quote = FALSE, sep = '\t', row.names = FALSE)
```

## Commands

Stata commands:

```
* Load data
insheet using "/Users/lcollado/Desktop/helpAG.txt"

* Model with interaction
xi: regress sales yearcen i.intervention*i.machine

* MLRs without interaction
regress sales yearcen i.intervention if machine == "EPIC"
regress sales yearcen i.intervention if machine == "MP"
```

## Output


Stata log:

```
. insheet using "/Users/lcollado/Desktop/helpAG.txt"
(5 vars, 10 obs)

. xi: regress sales yearcen i.intervention*i.machine
i.intervention    _Iintervent_0-1     (naturally coded; _Iintervent_0 omitted)
i.machine         _Imachine_1-2       (_Imachine_1 for machine==EPIC omitted)
i.int~n*i.mac~e   _IintXmac_#_#       (coded as above)

      Source |       SS       df       MS              Number of obs =      10
-------------+------------------------------           F(  4,     5) = 9349.41
       Model |  4.9067e+09     4  1.2267e+09           Prob > F      =  0.0000
    Residual |  656013.863     5  131202.773           R-squared     =  0.9999
-------------+------------------------------           Adj R-squared =  0.9998
       Total |  4.9073e+09     9   545258827           Root MSE      =  362.22

-------------------------------------------------------------------------------
        sales |      Coef.   Std. Err.      t    P>|t|     [95% Conf. Interval]
--------------+----------------------------------------------------------------
      yearcen |  -18.38291   161.9894    -0.11   0.914    -434.7898     398.024
_Iintervent_1 |   20177.55   522.8184    38.59   0.000      18833.6     21521.5
  _Imachine_2 |  -29982.61   362.2192   -82.77   0.000    -30913.72   -29051.49
_IintXmac_1_2 |  -20110.96    467.623   -43.01   0.000    -21313.02   -18908.89
        _cons |   39937.35    268.629   148.67   0.000     39246.82    40627.88
-------------------------------------------------------------------------------

. regress sales yearcen i.intervention if machine == "EPIC"

      Source |       SS       df       MS              Number of obs =       5
-------------+------------------------------           F(  2,     2) =  812.40
       Model |   486375001     2   243187500           Prob > F      =  0.0012
    Residual |   598685.85     2  299342.925           R-squared     =  0.9988
-------------+------------------------------           Adj R-squared =  0.9975
       Total |   486973687     4   121743422           Root MSE      =  547.12

------------------------------------------------------------------------------
       sales |      Coef.   Std. Err.      t    P>|t|     [95% Conf. Interval]
-------------+----------------------------------------------------------------
     yearcen |  -123.0898   346.0306    -0.36   0.756    -1611.939     1365.76
1.interven~n |   20439.32   998.9043    20.46   0.002     16141.38    24737.25
       _cons |    39989.7   423.7992    94.36   0.000     38166.24    41813.16
------------------------------------------------------------------------------

. regress sales yearcen i.intervention if machine == "MP"

      Source |       SS       df       MS              Number of obs =       5
-------------+------------------------------           F(  2,     2) =    7.62
       Model |  19140.4723     2  9570.23614           Prob > F      =  0.1159
    Residual |  2510.30333     2  1255.15167           R-squared     =  0.8841
-------------+------------------------------           Adj R-squared =  0.7681
       Total |  21650.7756     4   5412.6939           Root MSE      =  35.428

------------------------------------------------------------------------------
       sales |      Coef.   Std. Err.      t    P>|t|     [95% Conf. Interval]
-------------+----------------------------------------------------------------
     yearcen |   86.32402   22.40671     3.85   0.061    -10.08427    182.7323
1.interven~n |  -195.1768    64.6826    -3.02   0.095    -473.4835    83.13001
       _cons |   9902.389    27.4425   360.84   0.000     9784.314    10020.46
------------------------------------------------------------------------------

. 
```



# Reproducibility

```{r}
options(width = 120)
devtools::session_info()
```



